%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Math \& SAT Tutor} % Job title
    {Orozco Tutoring} % Organization
    {San Diego, California} % Location
    {Jun. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Started my own tutoring business from zero clients and built a solid client base of students ranging from middle school to the college level.}
        \item {Kept track of performance and provided a guided curriculum to build a plan around each student.}
        \item {Self managed scheduling, invoicing, and communication to both students and parents.}
        \item {Students I tutored saw dramatic increases in grade level with an average of 15\% grade point increase for each student.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Open Source Software Contributor} % Job title
    {Mattermost} % Organization
    {github.com/mattermost} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved developer experience by migrating data access layer from being asynchronous to synchronous.}
        \item {Worked as a volunteer alongside the Mattermost Core team to ship features and fix bugs on software that tens of thousands of people use for daily team communication.}
        \item {Implemented features from the backend to the frontend while updating test cases and documentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst Intern} % Job title
    {Watsco, Inc} % Organization
    {Miami, Florida} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased efficiency in document retrieval by digitizing documents and creating an indexed database. This allowed coworkers to access a library of documents without leaving their desk.}
        \item {Implemented a distributed web stress test tool with high anonymity.}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
